%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{
EMCL Secretary \\
International Center for Computational Logic \\
Department of Computer Science\\
Technische Universität Dresden \\
01062 Dresden,
Germany} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf Samy Shihata \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
257 Miami, \\ Alexandria, Egypt 21111 \\ (002) 01095357548 % Your address and phone number
\end{center} 
\vfill

\signature{Samy Shihata} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{To whom it may concern,} 
 
  I would like to express my wish to join the European Master's Program in
  Computational Logic starting 2015.
  Allow me to provide some information that may further support my application.
  I am currently a senior Computer Science and Engineering student at the German
  University in Cairo.  I became interested in computer programming started
  early on. To me, programming was the ability to  materialize an idea
  using a few lines of code. I found it to be the ideal form of expression. I
  was also fascinated by the regular technological advances made daily in terms
  of both software and hardware. I began learning C at the age of twelve,
  followed by other languages such as C++, visual basic. I mainly practiced on
  small projects for my own use.  

  Following high school, I decided to follow a career in computer science. I was
  offered a partial scholarship to join the Bachelor Program in Computer Science
  and Engineering of the German University in Cairo.I am currently in my senior
  year and expected to graduate next semester with highest honors. I am
  currently ranked the second top student of my class with GPA: $0.89$ . My
  chosen study track was mainly focused on the Theory of Computation and
  Artificial Intelligence. I covered courses of Machine Learning, Knowledge
  Representation and Reasoning, First Order Logic, Analysis and Design of
  Algorithms and Declarative and Functional
  programming. I also included some general courses such as Software Engineering
  and Computer Graphics. During my study, I attended several extra-curricular courses and
  workshops abroad such as the CHR workshop 2013 in Berlin. These trips were
  funded by my university as a reward of academic excellence. Finally, I did my
  Bachelor Project during my stay in Augsburg university as an exchange student,
  under the supervision of Prof. Dr. Elizabeth Andre. My Thesis was titled the
  Emotion Classification: Sentimental Analysis over EEG. My stay there was also
  funded by my university.

  While I was involved in several internships relating to web development,
  including a website for the university itself, my main interest have always
  been Artificial Intelligence. I view research in AI as the gateway towards the
  most advanced computation device in existence, the human brain. For that I have
  tried to become part of the AI research community. I have taken several
  internships relating to the field such as Machine Learning text classification
  with Intel Egypt. Currently, I am part of an effort to start an Artificial
  Intelligence research group in the German University in Cairo, in which I am
  mainly responsible of Machine Learning and Data Mining research.
  
  In order to pursue a career in AI research, I decided to take a Master's program in
  Computational Logic. Many breakthroughs in AI are attributed to new
  developments in logical theory. New generation expert systems rely heavily on
  logic for reasoning and representing their often very large and complex
  Knowledge bases. Problems such as planning, natural language processing as
  well as the abstract concepts of rationality and common sense, all require
  a strong logical framework to be able to understand them.

  After reviewing the top universities that offer a Master's Program in
  Computational Logic, I find that the European program is the most suited one
  for my goals. First, having gone over the list of publications created during
  the study of EMCL, its clear to me that the program is research directed
  encouraging true contributions to the field. Also the program's connection
  with some of the most renowned research universities guarantees exceptional
  standards of education. Having been in Germany before, for some study courses,
  I am familiar with the European attitude towards learning which makes it both
  a more challenging and rewarding experience. Regarding the content of the
  program, I am particularly interested in the Constraint Programming module,
  having had previous experience with CHR. I am also eager to get more in depth
  Knowledge into both knowledge representation and Inference.

  In conclusion, I would like to point out that I am a hard working student,
  eager to learn and will be happy to prove my worth should I be given the
  opportunity to join this program. I believe that I will truly benefit from
  such an opportunity and in return I would be able to be of benefit to the
  scientific and research community.

\closing{Thank you for your consideration,}

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
