\documentclass{article}

\title{ Courses not yet included in my Transcript}
\author{Samy Shehata}
\begin{document}
\maketitle

This is a list of courses that I am currently taking in my senior year, and so
not yet included in my official transcript attached with the application. How-
ever, these courses will be included in the final transcript.

\begin{enumerate}
  \item \textbf{Name of the course:} Introduction to Artificial Intelligence\\
    \textbf{Course content:}\\
    History and philosophical foundations of AI, intelligent agents, problem
    solving by searching, propositional logic, predicate logic, resolution,
    logical
    reasoning systems, planning and acting.

    
  \item \textbf{Name of the course:} Computer Vision\\
    \textbf{Course content:}\\
    Image enhancement, image operations, image filtering, feature detectors,
    image analysis, classification, labeling, segmentation, pyramidal architecture, morphology, projective geometry, stereo vision, point matching, 3D
    reconstruction, object recognition and tracking.

  \item \textbf{Name of the course:} Neural Networks\\
    \textbf{Course content:}\\
     Basics of neural networks computing, neural networks models and learning
     methods.

  \item \textbf{Name of the course:} Knowledge Representation and Reasoning\\
    \textbf{Course content:}\\
What is ``knowledge'', ''representation``, and ``reasoning``, propositional
logic, first order logic, formalizing commonsense reasoning, model logic,
non-monotonic logic, the logic of time, belief change and reason maintenance and the logic of causality.

  \item \textbf{Name of the course:} Computer and Network Security\\
    \textbf{Course content:}\\
Security planning, security policies, introduction to cryptography,
authentication functions, computational cryptography, symmetric encryption,
asymmetric encryption, hash functions, symmetric key exchange protocols,
asymmetric key-distribution, network layer security, internet protocol security, internet key exchange, transport layer security, application
layer security and wireless network security.

  \item \textbf{Name of the course:} Compilers\\
    \textbf{Course content:}\\
   Lexical analysis, regular expressions, finite automata, syntax analysis, top
   down parsing, bottom up parsing, semantic analysis, top checking, symbol table, intermediate code generation, syntax directed translation, three
   address, code generation and optimization.

  \item \textbf{Name of the course:} Machine Learning\\
    \textbf{Course content:}\\
    Probability Theory and linear algebra, linear classifiers, non linear
    classifiers, unsupervised learning, feature extraction, dimensionality reduction
    and reinforcement learning.


  \item \textbf{Name of the course:} Mathematical Optimization \\
    \textbf{Course content:} \\
    Optimization techniques for different types of functions including global
    optimization techniques, such as simulated annealing and genetic algorithms,
    linear programming, as well as local optimization functions such as
    quasi-Newton and Nelder-Mead.

    
  \item \textbf{Name of the course:} Advanced Computer Lab \\
    \textbf{Course content:}
Audio compression and psycho-acoustic
model, introduction to Sphinx4 speech recognition engine, speech recognition and
performance testing, corpora preparation and training acoustic models, speaker
independent speech recognition and building a dialogue system using voiceXML.


  \item \textbf{Name of the course:} Compilers Lab \\
    \textbf{Course content:}
   Implementing lexical analyzers, syntactic analyzers and semantic analyzers
   from scratch as well as using the relevant automation tools. It also covers
   generating code into byte code or MIPS assembly. 

  
    \end{enumerate}

\enddocument
